Models

### 2021-10-19 analysis/05_model_metrics.Rmd
Add a column that checks p-value and confidence interval significance.

```{r}
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lmerTest)
```
#### Read in data, get final dataset for models
Get data and put it in long form 
```{r}
pins::board_register_github(repo = "karinorman/biodivTS_data", branch = "master")

@@

metric_model_table <- bind_rows(mod_results %>% filter(is.na(warning)), 
          bad_mod_results %>% filter(is.na(warning)))

@@

model_df <- metric_model_table %>%
  select(metric, model, model_id) %>%
  group_by(metric, model_id) %>% 
  slice_head()

>>>>

```{r}
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lmerTest)
library(emmeans)
```
#### Read in data, get final dataset for models
Get data and put it in long form 
```{r}
pins::board_register_github(repo = "karinorman/biodivTS_data", branch = "master")

@@

metric_model_table <- bind_rows(mod_results %>% filter(is.na(warning)), 
          bad_mod_results %>% filter(is.na(warning))) %>%
  mutate(significant = case_when(
    p.value > 0.05 | lower.CL < 0 & upper.CL > 0 ~ FALSE,
    !is.na(p.value) | !is.na(lower.CL) ~ TRUE,
    TRUE ~ NA
  ))

@@

model_df <- metric_model_table %>%
  filter(model_id == "base") %>%
  select(metric, model, model_id) %>%
  group_by(metric, model_id) %>% 
  slice_head()
